Dimensionality

### 2020-08-04 main_figures/dimensionality.Rmd
forgotten commit...

p3 <- renameHrows(
  evalHeatmap( res, what=c("NMI","min_pr"), agg.by=c("norm","dims"), 
               filter=sel=="sel.vst" & !(dims %in% c("10","30","essLocal.b")),
                   row_split=gsub("norm\\.","",norm), reorder_rows=TRUE, anno_legend=FALSE,
               row_names_max_width = unit(6.2, "cm")) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dims"), row_split=gsub("norm\\.","",norm), 
              filterExpr=n_clus==true.nbClusts & sel=="sel.vst" & !(dims %in%                                                                      c("10","30","essLocal.b")), row_names_max_width = unit(6.2, "cm"),
              reorder_rows=TRUE, anno_legend=FALSE, title="ARI at\ntrue k"),
  rnfn
)
p3 <- grid.grabExpr(draw(p3, annotation_legend_list=.scaledLegend(), merge_legend=TRUE, heatmap_legend_side="bottom"))
```

>>>>

res$evaluation$clustering <- res$evaluation$clustering[!(res$evaluation$clustering$dims %in% c("10","30","essLocal.b")),]

p3 <- renameHrows(
  evalHeatmap( res, what=c("MI","ARI"), agg.by=c("norm","dims"), 
                   row_split=gsub("norm\\.","",norm), reorder_rows=TRUE, anno_legend=FALSE,
               row_names_max_width = unit(6.2, "cm")) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dims"), row_split=gsub("norm\\.","",norm), 
              row_names_max_width = unit(6.2, "cm"),
              filterExpr = n_clus==true.nbClusts,
              reorder_rows=TRUE, anno_legend=FALSE, title="ARI at\ntrue k"),
  function(x){
    x <- rnfn(sapply(strsplit(x," > "), FUN=function(x) rev(x)[1]))
  }
)
p3 <- grid.grabExpr(draw(p3, annotation_legend_list=.scaledLegend(), merge_legend=TRUE, heatmap_legend_side="bottom"))
```
